\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-21 document/XSGRB_sample.tex

	\subsection{GRB120327A (z = 2.813)}
	The data presented here also formed the basis of GCN \#
	13134\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/13134.gcn3}} and is published
	in \citet{DElia2014}.
	Consisting of two observations, 2.13 hrs and 29.98 hrs after the burst,
	continuum is visible in all arms for both.
	Absorption features from Ly-limit, \lya, \cii/\cii$^*$, \SIii/\SIii$^*$, \ali,
	\feii ~and \mgii ~are detected at a consistent redshift, $z = 2.813$.

>>>>

	\subsection{GRB120327A (z = 2.813)}
	The data presented here also formed the basis of GCN \#
	13134\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/13134.gcn3}} and is published
	in \citet{DElia2014}.
	The observation consists of two visits, 2.13 hrs and 29.98 hrs after the burst,
	with an afteglow continuum visible in all arms for both visits.
	We detect absorption features from Ly-limit, \lya, \cii/\cii$^*$, \SIii/\SIii$^*$, \ali,
	\feii ~and \mgii ~are detected at a consistent redshift, $z = 2.813$.

        \subsection{GRB130408A (z = 3.758)}
	The data presented here also formed the basis of GCN \#
	14365\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/14365.gcn3}}. The spectrum 
	has not otherwise been published previously.
	The observations consists of two 600sec spectra taken 1.9hr after the burst.
	We detect absorption features from a wide range of ions. We also detect intervening absorption at $z=1.255$
	and $z=3.248$.
